### 2014-05-21 intro.tex
Hangout -> Hangouts

\begin{center}
\noindent \begin{tabular}{|l|c|c|}
\hline
Sprout vs. & Avg.~speedup & Delay reduction \\
\hline
\hline
Skype & $2.2\times$ & $7.9\times$\\
Hangout & $4.4\times$ & $7.2\times$\\
Facetime & $1.9\times$ & $8.7\times$\\
\hline
Compound & $1.3\times$ & $4.8\times$\\
TCP Vegas & $1.1\times$ & $2.1\times$\\
LEDBAT & no change & $2.8\times$\\
Cubic & \cellcolor{red!20}$0.91\times$ & $79\times$\\
%\hline
%Cubic-CoDel & \cellcolor{red!20}$0.70\times$ & $1.6\times$ (0.50~s) \\
%CUBIC/CoDel & & \\
%Compound/CoDel & & \\
\hline
\end{tabular}

@@

Congestion-control protocols are often evaluated for their
TCP-friendliness~\cite{friendlysurvey}, or in other words, for how
well they share a contended network resource with traditional TCP
flows as another TCP would.  By default, RemyCCs do not
play well with TCP on the same bottleneck---they are too deferential
and end up receiving less than their fair share.\footnote{RemyCCs
  generally try to keep standing queues small, both because we provide
  Remy with an objective that penalizes excess delay, but also because
  the shorter the queueing delay, the quicker the convergence time and
  the greater the throughput available to new flows. A long-running
  traditional TCP flow will work to fill queues until they overflow.}

@@

\begin{center}
\includegraphics[width=0.75 \textwidth]{homo-3.pdf}
\end{center}

@@

\begin{center}
\includegraphics[width=0.75 \columnwidth]{oprange-manual.pdf}
\end{center}

>>>>

\begin{center}
\noindent \begin{tabular}{|l|c|c|}
\hline
Sprout vs. & Avg.~speedup & Delay reduction \\
\hline
\hline
Skype & $2.2\times$ & $7.9\times$\\
Hangouts & $4.4\times$ & $7.2\times$\\
Facetime & $1.9\times$ & $8.7\times$\\
\hline
Compound & $1.3\times$ & $4.8\times$\\
TCP Vegas & $1.1\times$ & $2.1\times$\\
LEDBAT & no change & $2.8\times$\\
Cubic & \cellcolor{red!20}$0.91\times$ & $79\times$\\
%\hline
%Cubic-CoDel & \cellcolor{red!20}$0.70\times$ & $1.6\times$ (0.50~s) \\
%CUBIC/CoDel & & \\
%Compound/CoDel & & \\
\hline
\end{tabular}

@@

Congestion-control protocols are often evaluated for their
TCP-friendliness~\cite{friendlysurvey}, or in other words, for how
well they share a contended network resource with traditional TCP
flows as another TCP would.  By default, RemyCCs do not
play well with TCP on the same bottleneck---they are too deferential
and end up receiving less than their fair share.\footnote{RemyCCs
  generally try to keep standing queues small, both because we provide
  Remy with an objective that penalizes excess delay, but also because
  the shorter the queueing delay, the quicker the convergence time and
  the greater the throughput rapidly available to new flows. A long-running
  traditional TCP flow will work to fill queues until they overflow.}

@@

\begin{center}
\includegraphics[width=0.95 \textwidth]{homo-3.pdf}
\end{center}

@@

\begin{center}
\includegraphics[width=0.95 \columnwidth]{oprange-manual.pdf}
\end{center}

### 2014-05-21 sprout_eval.tex
Hangout -> Hangouts

This section presents our experimental results obtained using the
testbed described
in \S\ref{ss:platform}. We start by motivating and defining the two
main metrics: throughput and self-inflicted delay. We then compare
Sprout with Skype, Facetime, and Hangout, focusing on how the
different rate control algorithms used by these systems affect the
metrics of interest. We compare against the delay-triggered congestion
control algorithms TCP Vegas and LEDBAT, as well as the
default TCP in Linux, Cubic, which does not use delay as a
congestion signal, and Compound TCP, the default in some
versions of Windows.

@@

We also observe that Skype, Facetime, and Google Hangout all have
lower throughput and higher delay than the TCP congestion-control
algorithms. We believe this is because they do not react to rate
increases and decreases quickly enough, perhaps because they are
unable to change the encoding rapidly, or unwilling for perceptual
reasons.\footnote{We found that the complexity of the video signal did
  not seem to affect these programs' transmitted throughputs. On fast
  network paths, Skype uses up to 5 Mbps even when the image is
  static.} By continuing to send when the network has dramatically
slowed, these programs induce high delays that destroy interactivity.

>>>>

This section presents our experimental results obtained using the
testbed described
in \S\ref{ss:platform}. We start by motivating and defining the two
main metrics: throughput and self-inflicted delay. We then compare
Sprout with Skype, Facetime, and Hangouts, focusing on how the
different rate control algorithms used by these systems affect the
metrics of interest. We compare against the delay-triggered congestion
control algorithms TCP Vegas and LEDBAT, as well as the
default TCP in Linux, Cubic, which does not use delay as a
congestion signal, and Compound TCP, the default in some
versions of Windows.

@@

We also observe that Skype, Facetime, and Google Hangouts all have
lower throughput and higher delay than the TCP congestion-control
algorithms. We believe this is because they do not react to rate
increases and decreases quickly enough, perhaps because they are
unable to change the encoding rapidly, or unwilling for perceptual
reasons.\footnote{We found that the complexity of the video signal did
  not seem to affect these programs' transmitted throughputs. On fast
  network paths, Skype uses up to 5 Mbps even when the image is
  static.} By continuing to send when the network has dramatically
slowed, these programs induce high delays that destroy interactivity.

### 2014-05-21 sprout_impl.tex
Lowercase section headings
Fixes to Remy section
Hangout -> Hangouts

\section{Experimental Testbed}
\label{s:impl}
\label{ss:platform}
We use trace-driven emulation to evaluate Sprout and compare it with
other applications and protocols under reproducible network
conditions. Our goal is to capture the variability of cellular
networks in our experiments and to evaluate each scheme under the same
set of time-varying conditions.

@@

@@

%\scriptsize
\noindent \begin{tabular}{|l|l|l|l|}
\hline
Program & Version & OS & Endpoints \\
\hline
\hline
Skype & 5.10.0.116 & Windows 7 & Core i7 PC \\
Hangout & as of 9/2012 & Windows 7 & Core i7 PC \\
Facetime & 2.0 (1070) & OS X 10.8.1 & MB Pro (2.3 GHz i7),\\
& & & MB Air (1.8 GHz i5) \\
TCP Cubic & in Linux 3.2.0 & & Core i7 PC \\
TCP Vegas & in Linux 3.2.0 & & Core i7 PC \\
LEDBAT & in $\mu$TP & Linux 3.2.0 & Core i7 PC \\
Compound TCP & in Windows 7 & & Core i7 PC \\
\hline
\end{tabular}

>>>>

\section{Experimental testbed}
\label{s:impl}
\label{ss:platform}
We use trace-driven emulation to evaluate Sprout and compare it with
other applications and protocols under reproducible network
conditions. Our goal is to capture the variability of cellular
networks in our experiments and to evaluate each scheme under the same
set of time-varying conditions.

@@

\label{ss:saturator}

@@

%\scriptsize
\noindent \begin{tabular}{|l|l|l|l|}
\hline
Program & Version & OS & Endpoints \\
\hline
\hline
Skype & 5.10.0.116 & Windows 7 & Core i7 PC \\
Hangouts & as of 9/2012 & Windows 7 & Core i7 PC \\
Facetime & 2.0 (1070) & OS X 10.8.1 & MB Pro (2.3 GHz i7),\\
& & & MB Air (1.8 GHz i5) \\
TCP Cubic & in Linux 3.2.0 & & Core i7 PC \\
TCP Vegas & in Linux 3.2.0 & & Core i7 PC \\
LEDBAT & in $\mu$TP & Linux 3.2.0 & Core i7 PC \\
Compound TCP & in Windows 7 & & Core i7 PC \\
\hline
\end{tabular}

### 2014-05-21 sprout_intro.tex
Add some results to sprout section of intro
Make Leslie fixes through end of Sprout
Hangout -> Hangouts

\section{Introduction}
\label{sprout:intro}

@@

Our experiments with Microsoft's Skype, Google's Hangout, and Apple's
Facetime running over traces from commercial 3G and LTE networks show
the shortcomings of the transport protocols in use and the lack of
adaptation required for a good user experience.
%(\S\ref{s:problem}). 
The transport protocols deal with rate variations in a reactive
manner: they attempt to send at a particular rate, and if all goes
well, they increase the rate and try again. They are slow to
decrease their transmission rate when the link has deteriorated, and as a
result they often create a large backlog of queued packets in the
network. When that happens, only after several seconds and a
user-visible outage do they switch to a lower rate.
%The
%encoder pre-determines which frames should be sent at any given
%encoding rate, not adapting to what the receiver might (or might not)
%have recently received.

@@

%\paragraph{Summary of results.}
We conducted a trace-driven experimental evaluation (details in
\S\ref{sprout:eval}) using data collected from four different commercial
cellular networks (Verizon's LTE and 3G 1xEV-DO, AT\&T's LTE, and
T-Mobile's 3G UMTS). We compared Sprout with Skype, Hangout, Facetime,
and several TCP congestion-control algorithms, running in both
directions (uplink and downlink).

@@

\begin{figure}
\caption{Sprout compared with other end-to-end schemes. Metrics where
  Sprout did not outperform the existing algorithm are highlighted in
  red.}
\label{f:sproutcompe2e}

\begin{center}
\noindent \begin{tabular}{|l|c|c|}
\hline
App/protocol & Avg.~speedup & Delay reduction \\
& \footnotesize{vs.~Sprout} & \footnotesize{(from avg.~delay)}\\
\hline
\hline
\cellcolor{blue!20}Sprout & \cellcolor{blue!20}$1.0\times$ & \cellcolor{blue!20}$1.0\times$ (0.32~s) \\
\hline
Skype & $2.2\times$ & $7.9\times$ (2.52~s) \\
Hangout & $4.4\times$ & $7.2\times$ (2.28~s) \\
Facetime & $1.9\times$ & $8.7\times$ (2.75~s) \\
\hline
Compound & $1.3\times$ & $4.8\times$ (1.53~s) \\
TCP Vegas & $1.1\times$ & $2.1\times$ (0.67~s) \\
LEDBAT & $1.0\times$ & $2.8\times$ (0.89~s) \\
Cubic & \cellcolor{red!20}$0.91\times$ & $79\times$ (25~s)\\
\hline
Cubic-CoDel & \cellcolor{red!20}$0.70\times$ & $1.6\times$ (0.50~s) \\
%CUBIC/CoDel & & \\
%Compound/CoDel & & \\
\hline
\end{tabular}
\end{center}

>>>>

%\section{Introduction}
\label{sprout:intro}

@@

Our experiments with Microsoft's Skype, Google's Hangouts, and Apple's
Facetime running over traces from commercial 3G and LTE networks show
the shortcomings of the transport protocols in use and the lack of
adaptation required for a good user experience.
%(\S\ref{s:problem}). 
The transport protocols deal with rate variations in a reactive
manner: they attempt to send at a particular rate, and if all goes
well, they increase the rate and try again. They are slow to
decrease their transmission rate when the link has deteriorated, and as a
result they often create a large backlog of queued packets in the
network. When that happens, only after several seconds and a
user-visible outage do they switch to a lower rate.
%The
%encoder pre-determines which frames should be sent at any given
%encoding rate, not adapting to what the receiver might (or might not)
%have recently received.

@@

%\paragraph{Summary of results.}
We conducted a trace-driven experimental evaluation (details in
\S\ref{sprout:eval}) using data collected from four different commercial
cellular networks (Verizon's LTE and 3G 1xEV-DO, AT\&T's LTE, and
T-Mobile's 3G UMTS). We compared Sprout with Skype, Hangouts, Facetime,
and several TCP congestion-control algorithms, running in both
directions (uplink and downlink).

@@

\begin{figure}
\caption{Sprout compared with other end-to-end schemes. Measurements where
  Sprout did not outperform the existing algorithm are highlighted in
  red.}
\label{f:sproutcompe2e}

\begin{center}
\noindent \begin{tabular}{|l|c|c|}
\hline
App/protocol & Avg.~speedup & Delay reduction \\
& \footnotesize{vs.~Sprout} & \footnotesize{(from avg.~delay)}\\
\hline
\hline
\cellcolor{blue!20}Sprout & \cellcolor{blue!20}$1.0\times$ & \cellcolor{blue!20}$1.0\times$ (0.32~s) \\
\hline
Skype & $2.2\times$ & $7.9\times$ (2.52~s) \\
Hangouts & $4.4\times$ & $7.2\times$ (2.28~s) \\
Facetime & $1.9\times$ & $8.7\times$ (2.75~s) \\
\hline
Compound & $1.3\times$ & $4.8\times$ (1.53~s) \\
TCP Vegas & $1.1\times$ & $2.1\times$ (0.67~s) \\
LEDBAT & $1.0\times$ & $2.8\times$ (0.89~s) \\
Cubic & \cellcolor{red!20}$0.91\times$ & $79\times$ (25~s)\\
\hline
Cubic-CoDel & \cellcolor{red!20}$0.70\times$ & $1.6\times$ (0.50~s) \\
%CUBIC/CoDel & & \\
%Compound/CoDel & & \\
\hline
\end{tabular}
\end{center}
